Incremental tactics

### 2012-05-05 doc/papers/LFMTP2012/paper.tex
paper

\usepackage{ntheorem}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{macros}
\usepackage{mathpartir}

@@

\title{Certified incremental program transformations}
%\subtitle{Subtitle Text, if any}

@@

  \caption{Typing algorithm}
  \label{fig:typing-algo}
\end{figure*}

% TODO example

@@

We now turn to the definition of our computation calculus. As we saw,
it is attached to special, \emph{defined} constants in the signature
and manipulates \LF\ objects. This language is un(i)typed, in that all
\LF\ objects have the same implicit type $\cst{obj}$. We have the
ability to construct objects out of other, and deconstruct them by
case analysis.
\begin{align*}
  T &\gequal
  \lam x T \gor
  U \\
  U &\gequal
  F \gor
  \matchin U \Gamma \casenobar {\app {\cst c} {\vec x}} U\ |\ \ldots\
  \case {\app {\cst c} {\vec x}} U
\end{align*}

>>>>

\usepackage{ntheorem}
\usepackage{amsmath}
\usepackage{amssymb}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\usepackage{macros}
\usepackage{mathpartir}
\usepackage{url}

@@

\title{Incremental tactics}
%\subtitle{Subtitle Text, if any}

@@

  \caption{Typing algorithm for the core calculus}
  \label{fig:typing-algo}
\end{figure*}

The main judgement is application typing $\jf\mr\Gamma F \mmr M A$,
which means that in repository $\mr$ and environment $\Gamma$, the
applicative term $F$ is well-typed of type $A$, and the slicing of $F$
produces a new repository $\mmr$. The object $M$ is the
\emph{residual} of this operation: only certain kind of applications
are sliced, and it is possible that the ``tip'' of application $F$ is
not sliced (because it is declared as non-sliceable). In that case,
$M$ is this tip; if $F$ is directly sliceable, then $M$ is the
metavariable referring to it.

Definitional equality judgement between two families $\jea\mr\Gamma A
{A'}$ is used by these typing rules. This equivalence is usually
defined to be just $\alpha$-equivalence since our objects are in
$\beta\eta$-canonical form. Here, objects can contain metavariables
defined in $\mr$, so we shall thread it. Moreover, we will see in next
section how defined constants compute and thus influence definitional
equality. Definitional equality is defined later in

\paragraph{Example}

Let us work out an example.
% TODO example

@@

We now turn to the definition of our computation calculus. As we saw,
it is attached to special, \emph{defined} constants in the signature
and manipulates \LF\ objects. This language is un(i)typed, in that all
\LF\ objects have the same implicit type $\cst{obj}$. We have the
ability to construct objects out of other, and deconstruct them by
case analysis:
\begin{align*}
  T &\gequal
  \lam x T \gor
  U \\
  U &\gequal
  F \gor
  \matchin U \Gamma \casenobar {\app {H} {\vec x}} U\ |\ \ldots\
  \case {\app {H} {\vec x}} U
\end{align*}

\begin{figure*}
  \centering
  TODO
  \caption{Weak head-reduction}
  \label{fig:whr}
\end{figure*}

\begin{figure*}
  \centering
  TODO
  \caption{Definitional equality}
  \label{fig:def-eq}
\end{figure*}
